Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-07 response/response.tex

``I would have expected that you randomly collected 1300 non-security commits to compare 
with the 1300 security commits.'': Although we started with 1300 commits, 
$331$ cases were tossed due to BCH limitations. In addition, BCH
takes substantial time to process this amount of cases. 
Since the comparison is between 
the final dataset of $969$ patches and the baselines. We produced d
baselines with the final number of viable results obtained for the security 
dataset.

We 
have collected a baseline of random changes only (no size restrictions) in the past and 
performed the same evaluation. We now present the results for both baselines: \textit{size-baseline}, where we consider
size appproximation; and, \textit{random-baseline}, where we consider all the regular
changes characteristics.

\begin{revcomment}[2.12]
    Section 3\\
    \begin{itemize}
        \item Since SIG seems to be "just another consulting organization" - I'd like 
        to see about the acceptance of the 10 guidelines in the software engineering 
        discipline.  I would guess you could find peer-reviewed references to support 
        these guidelines, or even books by Martin Fowler.   That has more credibility 
        than the reference by the SIG consulting group. For example on Page 9, line 42 
        you cite McCabe Complexity --  that has more credibility than a consulting 
        organizations guidelines that they use to make money on their tool.  Tell us more 
        about the BCH data experience since that is your comparison point for compliance.
    \end{itemize}
\end{revcomment}

\Us All the guidelines are fully described on their book ``Building Maintainable 
Software: Ten Guidelines for Future-Proof Code''
\footnote{Available here: \url{https://www.softwareimprovementgroup.com/resources/ebook-building-maintainable-software/}}.

We found other papers using some of the metrics measured by BCH. But we did not find
extra theoretical papers explaining metrics in detail as we found for McCabe Complexity.
However, metrics like Unit Size, Duplication, Unit Interfacing, Volume, Testability
and Code Smells are well-known metrics in the Software Engineering field.

We would like to address your concern regarding the credibility of BCH. BCH checks GitHub 
codebases against 10 engineering guidelines as devised by Software Improvement Group 
(SIG). SIG has devised these guidelines after many years of experience: analyzing more 
than 15 million lines of code every week, SIG maintains the industry’s largest 
benchmark, containing more than 10 billion lines of code across 200+ technologies; SIG 
is the only lab in the world certified by TÜViT to issue ISO 25010:2011 
certificates\footnote{Information available here: 
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/}}.

The underlying maintainability model for BCH is documented with several
(non-academic) reports linked at this page:
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/} as 
well as validated by the academic community in the following paper:

SIG performs the threshold calibration
yearly on a proprietary data set to satisfy the requirements of TUViT to
be a certified measurement model. However, please note that this data set 
cannot be shared due to non-disclosure agreements between SIG and its 
clients. BCH has a free plan available that allows the analysis of public
projects with a size limit of 100.000 lines of code.

### 2021-02-07 paper/emse20.tex
response to 2.12
improving study implications

\begin{table}[h]
\centering
\scriptsize
	\caption{Guidelines to produce maintainable code. \Sofia{Still need to add more references}}
\begin{tabular}{L{2cm}L{4.5cm}L{4cm}}

@@

\textit{\textbf{Tools for Patch Risk Assessment:}}
	Design debt of one guideline can lead to severe impacts on the 
	software quality~\cite{10.1145/1985362.1985366}. Some software 
	producers consider security as a first class citizen while others 
	do not. As mentioned in previous work, security it is very important 
	and should bee considered as a default feature~\cite{10.1145/2489828.2489830,kurilova2014wyvern,mcgraw2004software}. 
	However, the lack of experts or awareness to the ease of producing 
	vulnerable software leads companies to ship low quality software. 
	Providing automated tools to developers assess the risk of their 
	patches it is important to help companies shipping software of higher quality. 
	Tools like Better Code Hub and static analysis (e.g., 
	SonarQube, Codacy, ESLint, Infer, and more) can be leveraged 
	to assess the risk of patching vulnerabilities---alongside pull
	requests/code reviews. Static code analysis may be daunting due 
	to the number of rules and different effects
	on maintainability. BCH claims to use the top-$10$ of the guidelines
	with the highest effects on maintainability. Yet, static analysis 
	can be used to complement the BCH analysis by introducing
	the capability of vulnerability detection and support the prediction 
	and prevention of the risk of a patch of hindering maintainability.
%

>>>>

\begin{table}[h]
\centering
\scriptsize
	\caption{Guidelines to produce maintainable code.}
\begin{tabular}{L{2cm}L{4.5cm}L{4cm}}

@@

\textit{\textbf{Tools for Patch Risk Assessment:}}
	Design debt of one guideline can lead to severe impacts on the 
	software quality~\cite{10.1145/1985362.1985366}. Some software 
	producers consider security as a first class citizen while others 
	do not. As mentioned in previous work, security it is very important 
	and should be considered as a default feature~\cite{10.1145/2489828.2489830,kurilova2014wyvern,mcgraw2004software}. 
	However, the lack of experts and awareness to the ease of producing 
	vulnerable software leads companies to ship low quality software. 
	Providing automated tools to developers assess the risk of their 
  patches it is important to help companies shipping software of higher quality. 
  Bryan O’Sullivan, VP of Engineering at Facebook, advocated for new computer science
  risk models to detect vulnerabilities in scale and predict the level of security of the software under production in
  his talk “‘Challenges in Making Software Work at Scale”’ at FaceTAV’20.

	Tools like Better Code Hub can complement static analysis (e.g., 
  SonarQube, Codacy, ESLint, Infer, and more) to provide more information 
  to security engineers on the vulnerabilities per se and the risk of their patches
  ---alongside pull requests/code reviews.
  Static code analysis may be daunting due 
	to the number of rules and different effects
	on maintainability. BCH claims to use the top-$10$ of the guidelines
	with the highest effects on maintainability. Yet, static analysis 
	can be used to complement the BCH analysis by introducing
	the capability of vulnerability detection and support the prediction 
	and prevention of the risk of a patch of hindering maintainability.
%
